Scale Space Edge Detection

### 2018-03-05 paper.tex
Updated Julia code for lena picture and colortypes, also paper

%&pdflatex
\documentclass{article}
\usepackage[final]{nips_2017}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}

@@

>>>>

%&pdflatex
\documentclass{article}
\usepackage[final]{nips_2017}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{morefloats}
\usepackage{float}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{xcolor}

    % Define the coloring for keywords in Julia
    \lstdefinelanguage{Julia}%
    {morekeywords={abstract,break,case,catch,const,continue,do,else,elseif,%
        end,export,false,for,function,immutable,import,importall,if,in,%
        macro,module,otherwise,quote,return,switch,true,try,type,typealias,%
        using,while},%
        sensitive=true,%
        alsoother={$},%
        morecomment=[l]\#,%
        morecomment=[n]{\#=}{=\#},%
        morestring=[s]{"}{"},%
        morestring=[m]{'}{'},%
    }[keywords,comments,strings]%

    % Set the lstlistings to the Julia color scheme
    \lstset{
        basicstyle=\ttfamily,
        columns=fullflexible,
        frame=single,
        breaklines=true,
        language         = Julia,
        basicstyle       = \ttfamily,
        keywordstyle     = \bfseries\color{blue},
        stringstyle      = \color{magenta},
        commentstyle     = \color{ForestGreen},
        showstringspaces = false,
    }

@@

    Then the strength of the edges is found by computing the path integral over the maximal connected edge $\Gamma$ given by

    \begin{equation}
        G(\Gamma) = \int_{(x;t) \in \Gamma} \sqrt{(G_{\gamma}L)(x;t)} \,\, ds
    \end{equation}

    where $ds^2=dx^2+dy^2$.

\section{Implementation}
    For our implementation we will be using the following image to run our tests on

    \begin{figure}[H]
    \centering
        \includegraphics[scale=0.5]{Images/lena.jpg}
        \caption{Lena Image}
        \label{lena_o}
    \end{figure}

    Figure \ref{lena_o} is a standard test image for image processing and is good for our purposes since it contains a variety of different edges with different strengths.

    So what we first do is define our convolution functions that we will be using in code.

    \begin{lstlisting}
        function combine_kernels(kers...)
            return reduce(conv2, kers)
        end

        function convolve_image(I, kers...)
            kernel = combine_kernels(kers...)
            return imfilter(I, centered(kernel))
        end

        function convolve_scale_space(L, kers...)
            return mapslices(
                scale_slice -> convolve_image(scale_slice, kers...),
                L,
                (1,2)
            )
        end

        function convolve_gaussian(img, sigma)
            # The dimension of the convolution matrix
            length = 8*ceil(Int, sigma) + 1
            return imfilter(img, reflect(Kernel.gaussian((sigma, sigma), (length, length))))
        end
    \end{lstlisting}
